%-------------------------
% Resume in Latex
% Author : Peng Cheng
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://cpyeah.github.io/}{Peng Cheng}} & Email : \href{mailto:chengpengyeah@126.com}{chengpengyeah@126.com}\\
  \href{http://cpyeah.github.io/}{https://cpyeah.github.io/} & Mobile : \href{tel:18262622193}{18262622193} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Nanjing University Of Posts And Telecommunications}{Nanjing, Jiangsu}
        {Bachelor of Computer Science and Technology}{Sep. 2011 -- July. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Jiangsu Qianmi Network Technology Co.,Ltd.}{Nanjing, Jiangsu}
      {Senior Software Engineer}{Aug 2020 - Present}
      \resumeItemListStart
        \resumeItem{Qianmi Trading Center}
          {The Qianmi trading center connects users, merchants, commodities, marketing, inventory, accounting and other key business, which is the core of driving the whole transaction process. As Qianmi new retail backstage infrastructure, it covers two major production lines: online orders and cashier orders. The total order volume more than 110 million, the average daily order is more than 150,000, the seller merchant is more than 10,000, the system QPS is about 200 and P99 is about 70ms.}
        \resumeItem{Qianmi Open Platform}
          {Qianmi Open platform attracts excellent ISV and professional ERP manufacturers to join by opening API services, including goods, members, orders, logistics and other basic services API, and provides merchants with overall e-commerce solutions including but not limited to ERP, CRM, BI, commodity management, order management and logistics services. At present, the open platform has more than 5000 developers and more than 1000 applications. QPS is about 40.}
        \resumeItem{Qianmi Task Center}
          {In order to meet the task of mass data import and export, and all asynchronous tasks can be reflected in the same place. Qianmi Task Center has been built. So far, more than 200,000 tasks have been successfully carried out. At most, there are more than 100 tasks to be carried out at the same time.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Nanjing Profeta Intelligent Technology Co., Ltd.}{Nanjing, Jiangsu}
      {Team Leader}{Jan 2019 - Jun 2020}
      \resumeItemListStart
        \resumeItem{3D cloud IoT system}
          {3D cloud is a printer, loT monitoring system. Responsible for real-time monitoring of printer status changes, and data analysis and processing, generate print report. And can remotely control the start and stop of the printer and the abnormal alarm of the printer.}
      \resumeItemListEnd

    \resumeSubheading
      {Client Service International, Inc.}{Nanjing, Jiangsu}
      {Full Stack Engineer}{Jun 2015 - Dec 2018}
      \resumeItemListStart
        \resumeItem{Jiangsu Bank Direct selling Bank}
          {Direct selling bank is an Internet financial App that meets the needs of users' investment, consumption, loans and life services, and provides customers with a unique series of comprehensive application services.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Go Tiny URL Service}
      {Use the Go language to create a dedicated abbreviated URL service that converts a long link into a short link and redirects to the original link address when visiting the short link.}
    \resumeSubItem{Java Multithreaded Crawler}
      {Use the multithreaded crawler written by Java to complete the work of HTTP request, mock login, Cookie saving and HTML parsing. After the data is obtained, it is stored in the database, and when the data grows to a certain size, Elasticsearch is used to process and analyze the data, and a simple search engine is completed.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Java, Go, SQL, JavaScript}
    }
    \item{
      \textbf{Database}{: MySQL, Redis, DynamoDB, ElasticSearch}
    }
    \item{
      \textbf{Technologies}{: MQ, Spring, Distributed System, Micro Service, DevOps}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
